\documentclass{beamer}
\usetheme{Frankfurt}

\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{physics}
\usepackage{tikz}
\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{decorations.pathreplacing}

\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Span}{span}

\tikzset{photon/.style={decorate, decoration=snake, draw = yellow, ultra thick}}
\tikzset{brace/.style={decorate, decoration=brace}}

\title{Quantum Logic and the Orthocomplemented Lattice of Propositions}
\subtitle{A logic based approach to Bell's inequalities\cite{Burbano2017}}
\author[Iván Burbano]{Iván Mauricio Burbano Aldana}
\institute{Universidad de los Andes}
\date{\today}

\begin{document}

\begin{frame}

	\titlepage

\end{frame}

\begin{frame}

	\frametitle{Outline}
	\tableofcontents

\end{frame}

\section{EPR Paradox}

\begin{frame}

	\frametitle{Completeness of Quantum Mechanics}
	
	Einstein, Podolsy and Rosen, although weary of the success of quantum mechanics, wanted to probe its completeness\cite{Einstein1935}.
	
	\begin{itemize}
		
		\item In a complete physical theory every element of physical reality has a counterpart in the theory.		
		
		\item If we can predict with certainty the value of a physical cuantity without disturbing the system, then there exists an element of physical reality corresponding to this physical quantity.
		
	\end{itemize}

\end{frame}

\begin{frame}

	\frametitle{Let's Put It to the Test}

	Well, as we've learned from our mathematician friends, lets assume it is!
	
	\begin{block}{Heisenberg's Uncertainty Principle}

		If two observables are represented by operators which do not commute they cannot be measured simultaneously, i.e., they do not have a simultaneous physical reality\cite{Hall2013}.

	\end{block}	

\end{frame}

\begin{frame}[fragile]

	\frametitle{Photon Polarization}

	As an example consider the linear polarization of a photon.
	
	\begin{columns}
	
		\column{0.5\textwidth}
		\begin{itemize}
	
			\item Hilbert space $\mathbb{C}^2$;
			\item Vector state describing polarization along the angle $\theta$ 
			\begin{equation}
				\ket{\theta}=(\cos(\theta),\sin(\theta));
			\end{equation}
			\item Operator describing ``The polarization of the photon is along $\theta$''
			\begin{equation}
				P(\theta)=\dyad{\theta}.
			\end{equation}
					
		\end{itemize}
	
		\column{0.5\textwidth}
		\begin{tikzpicture}
			\draw[thin, ->] (-2,0) -- (2,0) node[right]{$\mathbb{C}$};
			\draw[thin, ->] (0,-2) -- (0,2) node[above]{$\mathbb{C}$};
			\draw[thin, dotted] (0,0) circle[radius=1.5];
			\draw[thick, ->] (0,0) -- ({1.5*cos(60)}, {1.5*sin(60)}) node[above right]{$\ket{\theta}$};
			\draw (0.25 ,0) arc (0:60:0.25);
			\draw (0.3, 0.3) node [right] {$\theta$};
		\end{tikzpicture}	

	\end{columns}

\end{frame}

\begin{frame}

	\frametitle{Two Photons}

	\begin{center}
		\begin{tikzpicture}
			\draw(0,0)node{Source}circle(0.7);
			\draw[photon](1,0)--(2.5,0);
			\draw[photon](-1,0)--(-2.5,0);
			\draw(3,0)ellipse(0.3 and 0.7);
			\draw(-3,0)ellipse(0.3 and 0.7);
			\begin{scope}
				\clip(-3,0)ellipse(0.3 and 0.7);
				\draw(-3,0)--(-2,2);
				\draw[dashed, ultra thin](-3,0)--(-3,1);
			\end{scope}
			\begin{scope}
				\clip(3,0)ellipse(0.3 and 0.7);
				\draw(3,0)--(4,1);
				\draw[dashed, ultra thin](3,0)--(3,1);
			\end{scope}
			\draw(-2.6,0.65)node{$\theta$};
			\draw(3.45,0.45)node{$\phi$};
			\draw(4,-0.7)rectangle(5.4,0.7);
			\draw(-4,-0.7)rectangle(-5.4,0.7);
			\draw(-4.7,0)node{$A$};
			\draw(4.7,0)node{$B$};
			\draw[brace](-5.4,1)--(-2.7,1);
			\draw[brace](2.7,1)--(5.4,1);
			\draw(-4.05,1.5)node{$P_A(\theta):=P(\theta)\otimes\id_{\mathbb{C}^2}$};
			\draw(4.05,1.5)node{$P_B(\phi):=\id_{\mathbb{C}^2}\otimes P(\phi)$};
	\end{tikzpicture}
	\end{center}
	
	We emmit two photons in the state
	\begin{align}
	\begin{split}
		\ket{\psi}=&\frac{1}{\sqrt{2}}(\ket{0}\otimes\ket{\pi/2}-\ket{\pi/2}\otimes\ket{0})\\
		=&\frac{1}{\sqrt{2}}(\ket{\pi/4}\otimes\ket{3\pi/4}-\ket{3\pi/4}\otimes\ket{\pi/4})\in\mathbb{C}^2\otimes\mathbb{C}^2.
	\end{split}
	\end{align}

\end{frame}

\begin{frame}

	\frametitle{Defeating Heisenberg's Uncertainty Principle}

	\begin{itemize}
	
		\item Knowledge of $P_B(0)\Rightarrow$ Knowledge of $P_A(0)$.		
		\item Knowledge of $P_B(\pi/4)\Rightarrow$ Knowledge of $P_A(\pi/4)$.
	
	\end{itemize}		

	Since $A$ and $B$ don't interact measurements of $B$ can't affect measurements of $A$!
	
\end{frame}

\begin{frame}

	\frametitle{Contradiction!}
	
	$P_A(0)$ and $P_A(\pi/4)$ have a simultaneous physical reality although $[P_A(0),P_A(\pi/4)]=0$!

\end{frame}

\section{Bell's Inequalities}

\begin{frame}

	\frametitle{The Search for a Complete Theory}
	
	Under the definitions given by EPR quantum mechanics is not complete. Can we provide a complete theory of physical reality? Bell while studying this question arrived at his inequalities for a theory of hidden variables\cite{Bell1964}. Our approach will be quite different.

\end{frame}
	
\begin{frame}

	\frametitle{Partially Ordered Sets}
	
	\begin{definition}
	
		A partially ordered set (poset) $(P,\leq)$ is a set $P$ along with a relation $\leq$ which is:
		\begin{itemize}
		
			\item reflexive: $p\leq p$ for all $p\in P$;
			\item anti-symmetric: $p\leq q$ and $q\leq p$ implies $p=q$ for all $p,q\in P$;
			\item transitive: $p\leq q$ and $q\leq r$ implies $p\leq r$ for all $p,q,r\in P$.   		
		
		\end{itemize}			
	
	\end{definition}
	
\end{frame}

\begin{frame}	
	

	\begin{example}	
		\begin{columns}	
	
			\column{0.5\textwidth}
			\begin{itemize}
	
				\item $(\mathbb{R},\leq)$
				\item $(P(X),\subseteq)$
				\item $(\text{Propositions},\Rightarrow)$!	
	
			\end{itemize}
		
			\column{0.5\textwidth}
			\begin{tikzpicture}
				\draw (-2,-2) -- (2,-2) -- (2,2) node[right]{$X$} -- (-2,2) -- (-2,-2);
				\filldraw[color = cyan!20] (0,-0.7) circle [radius=1];
				\filldraw[red!20] (0,-0.7) circle [radius=0.5];
				\filldraw[yellow!20, rotate = 30] (1,0) ellipse (0.7 and 0.5);
				\begin{scope}
					\clip (0,-0.7) circle [radius=1];
					\fill[blue!15, rotate = 30] (1,0) ellipse (0.7 and 0.5);
				\end{scope}				
				\draw (0.5,0.5) node{$C$};
				\draw (0,-0.7) node{$A$};
				\draw (0.7,-0.7) node{$B$};
			\end{tikzpicture}		
		
		\end{columns}
	\end{example}

\end{frame}	

\begin{frame}

	\frametitle{Meet and Join}
	
	\begin{definition}
	
		Let $(P,\leq)$ be a poset and $p,q\in P$. We define $p\wedge q$ to be the greatest lower bound of $\{p,q\}$ if it exists. Similarly $p\vee q$ is the least upper bound of $\{p,q\}$ if it exists.	If for every pair $p,q\in P$ both $p\wedge q$ and $p\vee q$ exist the poset is said to be a lattice.
	
	\end{definition}

\end{frame}

\begin{frame}

	\frametitle{Examples of Meets and Joins}
	
	\begin{example}
		
		\begin{columns}

			\column{0.5\textwidth}
			\begin{itemize}
		
				\item $(\mathbb{R},\leq)$ is a lattice where $x\wedge y=\min\{x,y\}$ and $x\vee y=\max\{x,y\}$.
		
				\item $(P(X),\subseteq)$ is a lattice where $A\wedge B=A\cap B$ and $A\vee B=A\cup B$.
		
			\end{itemize}	
			
			\column{0.5\textwidth}
			
				\begin{center}
				\begin{tikzpicture}[scale = 0.6]
				\draw(-2.8,-2.8)--(2.8,-2.8)--(2.8,2.8)node[above right]{$X$}--(-2.8,2.8)--(-2.8,-2.8);
				\fill[red!20](0,-1)circle[radius=1.6];
				\fill[blue!20](0,1)circle[radius=1.6];
				\begin{scope}
					\clip(0,-1)circle[radius=1.6];
					\fill[yellow!20](0,1)circle[radius=1.6];
				\end{scope}
				\draw(0,0)node{$A\cap B$};
				\draw(0,-1)node{$A$};
				\draw(0,1)node{$B$};
				\end{tikzpicture}		
				\end{center}
	
		\end{columns}	
		
	\end{example}

\end{frame}

\begin{frame}

	\frametitle{Meet and Join in $(\text{Propositions},\Rightarrow)$}
	
	\begin{example}
		$(\text{Propositions},\Rightarrow)$ form a lattice where $p\wedge q$ is the conjunction of the propositions and $p\vee q$ is the disjunction. Indeed,
		\begin{itemize}
			\item $p\wedge q\rightarrow p$ and $p\wedge q\Rightarrow q$ showing that $p\wedge q$ is a lower bound;
			\item if $r\Rightarrow p$ and $r\Rightarrow q$ then $r\Rightarrow p\wedge q$.
		\end{itemize}
	\end{example}

\end{frame}

\begin{frame}

	\frametitle{Some Properties of Meets and Joins}
	
	\begin{theorem}
	
		Let $(P,\leq)$ be a poset. For all $p,q,r\in P$:
		\begin{itemize}
			\item $p\leq q$ if and only if $p\wedge q = p$ if and only if $p\vee q=q$;
			\item (idempotency) $p\wedge p=p=p\vee p$.
		\end{itemize}			
	
	\end{theorem}

\end{frame}

\begin{frame}

	\frametitle{Boundedness}
	
	\begin{definition}
		
		A poset $(P,\leq)$ is said to be bounded if there is a greatest lower bound $0$ and a least upper bound $1$. A complement of $p\in P$ is an element $q\in P$ such that $p\wedge q=0$ and $p\vee q=1$		
		
	\end{definition}

\end{frame}

\begin{frame}

	\frametitle{Bounded and Unbounded Lattices}
	
	\begin{example}
		\begin{columns}
			\column{0.5\textwidth}
			\begin{itemize}
				\item $(\mathbb{R},\leq)$ is an unbounded lattice.
				\item $(P(X),\subseteq)$ is a bounded lattice in which $0=\emptyset$, $1=X$, and the complement of $A$ is $X\setminus A$.
				\item $(\text{Propositions},\Rightarrow)$ is a bounded lattice in which $0$ is always false, $1$ is always true, and the complement of a proposition $p$ is its negation $\neg p$.
			\end{itemize}
			\column{0.5\textwidth}
			\begin{tikzpicture}
				\fill[blue!20](-2,-2)rectangle(2,2);
				\fill[red!20](0,0)circle(1);
				\draw(-2,-2)node[above right]{$X\setminus A$};
				\draw(2,2)node[above right]{$X$};
				\draw(0,0)node{$A$};
			\end{tikzpicture}
		\end{columns}
	\end{example}

\end{frame}

\begin{frame}

	\frametitle{Distributivity}

	\begin{definition}
	
		A lattice $(L,\leq)$ is said to be distributive if $p\wedge(q\vee r)=(p\wedge q)\vee(p\wedge r)$ and $p\vee (q\wedge r)=(p\vee q)\wedge (p\vee r)$ for all $p,q,r\in L$.	
	
	\end{definition}

\end{frame}

\begin{frame}

	\frametitle{Distributivity in $(\text{Propositions},\Rightarrow)$}

	\center
	\begin{tabular}{|c|c|c|c|c|c|c|c|}
	\hline
	$p$ & $q$ & $r$ & $q\vee r$ & $p\wedge q$ & $p\wedge r$ & $p\wedge(q\vee r)$ & $(p\vee q)\wedge(p\vee r)$ \\
	\hline
	T & T & T & T & T & T & T & T \\
	T & T & F & T & T & F & T & T \\
	T & F & T & T & F & T & T & T \\
	T & F & F & F & F & F & F & F \\
	F & T & T & T & F & F & F & F \\
	F & T & F & T & F & F & F & F \\
	F & F & T & T & F & F & F & F \\
	F & F & F & F & F & F & F & F \\
	\hline
	\end{tabular}

\end{frame}

\begin{frame}

	\frametitle{Boolean Algebras}
	
	\begin{definition}
	
		A Boolean algebra is a distributive bounded lattice in which every element has a complement.	
	
	\end{definition}

	The complement of $p$ in a Boolean algebra will be denoted by $p'$.

	\begin{alertblock}{Interpretation}
		We will interpret EPR's requirements of a complete physical theory to be that the set of propositions one may ask of the theory be a Boolean algebra.
	\end{alertblock}

\end{frame}

\begin{frame}

	\frametitle{Coincidences}
	
	Let $(B,\leq)$ be a Boolean algebra. Define the coincidence function
	\begin{align}
	\begin{split}
		f:B\times B&\rightarrow B\\
		(p,q)&\mapsto f(p,q):=(p\wedge q)\vee(p'\wedge q').
	\end{split}
	\end{align}
	
\end{frame}

\begin{frame}

	\frametitle{Distributivity in Coincidences}

	Note that for all $p_1,q_1,p_2,q_2\in B$
	\begin{align}
	\begin{split}
		(p_1\wedge q_1)\wedge((p_1\wedge q_2)\vee(p_2'\wedge q_2')\vee(p_2\wedge q_1))=&\\
		(p_1\wedge q_1)\wedge((p_1\wedge q_2)\vee(p_2\vee q_2)'\vee(p_2\wedge q_1))=&\\
		(p_1\wedge q_1\wedge q_2)\vee(p_1\wedge q_1\wedge (p_2\vee q_2)')\vee(p_1\wedge q_1\wedge p_2)=&\\
		(p_1\wedge q_1)\wedge(q_2\vee(p_2\vee q_2)'\vee p_2)=(p_1\wedge q_1)\wedge 1=p_1\wedge q_1.&
	\end{split}
	\end{align}

\end{frame}
	
\begin{frame}
	
	\frametitle{Bell's Inequalities in Boolean Algebras}
	
	We conclude
	\begin{equation}
		p_1\wedge q_1\leq(p_1\wedge q_2)\vee(p_2'\wedge q_2')\vee(p_2\wedge q_1). 
	\end{equation}	
	Similarly
	\begin{equation}
		p_1'\wedge q_1'\leq(p_1'\wedge q_2')\vee(p_2\wedge q_2)\vee(p_2'\wedge q_1').
	\end{equation}
	Therefore
	\begin{theorem}[Bell's Inequalities for Boolean Algebras]
	
		Let $(B,\leq)$ be a Boolean algebra. For all $p_1,q_1,p_2,q_2$ we have
		\begin{equation}
			P(f(p_1,q_1))\leq P(f(p_1,q_2))+P(f(p_2,q_2))+P(f(p_2,q_1)).
		\end{equation}			
	
	\end{theorem}
	
\end{frame}		

\begin{frame}

	\frametitle{Degrees of Plausibility}
	
	In quantum mechanics we are more comfortable with the assignment of probabilities to propositions\cite{Jaynes2003}. Any reasonable assignment 
	\begin{equation}
		P:B\rightarrow [0,1]
	\end{equation}
	of degree of plausibility to physical propositions must be such that 
	\begin{itemize}
		\item $p\leq q\Rightarrow P(p)\leq P(q)$;
		\item (sum rule) $P(p\vee q)\leq P(p)+P(q)$.
	\end{itemize}.
	
\end{frame}

\begin{frame}

	\frametitle{Bell's Inequalities}

	\begin{theorem}[Bell's Inequalities]
	
		Let $(B,\leq)$ be a Boolean algebra with an assignation of degrees of plausibility $P$. Then
		\begin{equation}
			P(f(p_1,q_1))\leq P(f(p_1,q_2))+P(f(p_2,q_2))+P(f(p_2,q_1)).
		\end{equation}			
	
	\end{theorem}

\end{frame}

\section{Lattice of Propositions in Quantum Mechanics}

\begin{frame}

	\frametitle{What are Propositions in Quantum Mechanics?}
	
	Propositions in quantum mechanics should be observables with only two possible values when measured: True or False\cite{Wilce2012}.
	
	\begin{itemize}
	
		\item Observable $\rightarrow$ Self-adjoint operator
		
		\item Spectrum $\{\text{False},\text{True}\}\rightarrow\{0,1\}$	
	
	\end{itemize}
	
	\begin{definition}
	
		We define propositions in quantum mechanics to be the orthogonal projections $L(\mathcal{H}):=\{P\in\mathcal{B}(\mathcal{H})|P^2=P=P^*\}$.	
	
	\end{definition}

\end{frame}
	
\begin{frame}

	\frametitle{Geometry on Hilbert Spaces}
	
	Once again, much like mathematicians, given that it is not clear how to define a poset structure on $L(\mathcal{H})$ we have to proceed by duality.
	
	\begin{theorem}
	
		Every closed subspace of $\mathcal{H}$ is the image of an orthogonal projection. Conversely, the image of every orthogonal projection is a closed subspace of $\mathcal{H}$.	
	
	\end{theorem}
	
	We may thus understand $L(\mathcal{H})$ as the set of closed subspaces of $\mathcal{H}$.

\end{frame}	

\begin{frame}

	\frametitle{Partial Order on $L(\mathcal{H})$}
	
	We inherit the Poset structure from $P(\mathcal{H})$. 
	
	\begin{definition}
	
		The poset of propositions in quantum mechanics is $(L(\mathcal{H}),\subseteq)$.	
	
	\end{definition}

This forms a bounded lattice in which every element has a complement:

	\begin{columns}

		\column{0.5\textwidth}
		\begin{itemize}
	
			\item $P\wedge Q=P\cap Q$
			\item $P\vee Q = \overline{\Span (P\cup Q)}$
			\item $0=\{0\}$
			\item $1=\mathcal{H}$
			\item $P'$ is the projection onto $P^\bot$
	
		\end{itemize}

		\column{0.5\textwidth}
		\begin{tikzpicture}
			\draw[thin, ->] (-1,0) -- (1,0)node[right]{$\mathbb{C}$};
			\draw[thin, ->] (0,-1) -- (0,1)node[above]{$\mathbb{C}$};
			\draw[thick] (-1,-1) -- (1,1) node[above right]{$P$};
			\draw[thick] (-1,1) -- (1,-1) node[below right]{$P'$};
		\end{tikzpicture}

	\end{columns}
	
\end{frame}

\begin{frame}

	\frametitle{Useful Theorems for Calculations}
	
	\begin{theorem}
		
		Let $P,Q\in L(\mathcal{H})$. Then,
		\begin{itemize}
			\item $P\leq Q\Leftrightarrow P=PQ=QP$;
			\item if $P$ and $Q$ commute $P\wedge Q=PQ$ and $P\vee Q=P+Q-PQ$.		
		\end{itemize}
		
	\end{theorem}

\end{frame}

\begin{frame}

	\frametitle{Degrees of Plausibility in Quantum Mechanics}
	
	In quantum mechanics every state determines a degree of plausibility on $(L(\mathcal{H}),\subseteq)$. In particular, vector states $\ket{\psi}\in\mathcal{H}$ determine the degree of plausibility
	\begin{equation}
		P_\psi(P)=\ev{P}{\psi}.
	\end{equation}
	One verifies that if $P\leq Q$ then
	\begin{align}
	\begin{split}
		\|P\ket{\psi}\|^2=&\ev{P^2}{\psi}=\ev{P}{\psi}=P_\psi(P)=P_\psi(PQ)\\
		=&\ev{PQ}{\psi}\leq\|P\ket{\psi}\|\|Q\ket{\psi}\|\leq\|Q\ket{\psi}\|^2\\
		=&P_\psi(Q).
	\end{split}
	\end{align}

\end{frame}

\begin{frame}

	\frametitle{Back to EPR}
	
	Notice that $[P_A(\theta),P_B(\phi)]=0$. Thus the proposition we assign to their conjunction ``Alice measures polarization at an angle $\theta$ while Bob at an angle $\phi$'' is 
	\begin{equation}
		P_A(\theta)\wedge P_B(\phi)=P_A(\theta)P_B(\phi)=P(\theta)\otimes P(\phi)
	\end{equation}
	with an expected value
	\begin{equation}
		P_\psi(P_A(\theta)\wedge P_B(\phi))=\ev{P_A(\theta)P_B(\phi)}{\psi}=\frac{1}{2}\sin(\theta-\phi)^2.
	\end{equation}
	
\end{frame}

\begin{frame}

	\frametitle{Complements of Polarization}
	
	It makes sense to choose as complements $P_A(\theta)'=P_A(\theta+\pi/2)$ and $P_B(\theta)'=P_B(\theta+\pi/2)$. It is clear then that 
	\begin{equation}
		P(P_A(\theta)'\wedge P_B(\phi)')=\frac{1}{2}\sin(\theta-\phi)^2.
	\end{equation}
	
\end{frame}

\begin{frame}

	To calculate de disjunction, notice that
	\begin{align}
	\begin{split}
		(P_A(\theta)'\wedge P_B(\phi)')(P_A(\theta)\wedge P_B(\phi))&=\\
		P_A(\theta+\pi/2)P_B(\phi+\pi/2)P_A(\theta)P_B(\phi)&=\\
		(P(\theta+\pi/2)\otimes P(\phi+\pi/2))(P(\theta)\otimes P(\phi)))&=\\
		P(\theta+\pi/2)P(\theta)\otimes P(\phi+\pi/2)P(\phi)&=\\
		0=(P_A(\theta)\wedge P_B(\phi))(P_A(\theta)'\wedge P_B(\phi)')&.
	\end{split}
	\end{align}	 

\end{frame}

\begin{frame}

	\frametitle{Expectation of Coincidences}
	
	We obtain
	\begin{align}
	\begin{split}
	f(P_A(\theta),P_B(\phi))=&(P_A(\theta)\wedge P_B(\phi))\vee(P_A(\theta)'\wedge P_B(\phi)')\\
	=&P_A(\theta)\wedge P_B(\phi)+P_A(\theta)'\wedge P_B(\phi)'.
	\end{split}
	\end{align}
	
	Since expectation values are linear, 
	\begin{equation}
	P(f(P_A(\theta),P_B(\phi)))=\sin(\theta-\phi)^2.
	\end{equation}
	
\end{frame}

\begin{frame}

	\frametitle{Violation of Bell's Inequalities}
	
	Thus Bell's inequalities dictate	
	\begin{align}
	\begin{split}
	1=&\sin(0-\pi/2)^2=P(f(P_A(0),P_B(\pi/2)))\\
	\leq&P(f(P_A(0),P_B(\pi/6)))+P(f(P_A(\pi/3),P_B(\pi/6)))\\
	&+P(f(P_A(\pi/3),P_B(\pi/2)))\\
	=&\sin(0-\pi/6)^2+\sin(\pi/3-\pi/6)^2+\sin(\pi/3-\pi/2)^2\\
	=&3/4.
	\end{split}
	\end{align}

\end{frame}

\begin{frame}

	\frametitle{Conclusion}
	
	\Huge There is no correct physical theory whose propositions satisfy a Boolean algebra.

\end{frame}

\begin{frame}

	\frametitle{What failed?}
	
	\begin{theorem}
		
		In a distributive bounded lattice elements have at most one complement.		
		
	\end{theorem}
	
	\begin{proof}
	
		Suppose $q$ and $r$ are complements of $p$ in a distributive bounded lattice. Then
		\begin{equation}
			q=q\wedge 1=q\wedge(p\vee r)=(q\wedge p)\vee(q\wedge r)=0\vee(q\wedge r)=q\wedge r.
		\end{equation}			
		This $q\leq r$. Similarly one can show $r\leq q$. By anti-symmetry $q=r$.
	\end{proof}
	
\end{frame}

\begin{frame}

	\frametitle{Many Complements!}

	It is clear that in the bounded lattice $L(\mathcal{H})$ complements are not unique. Thus the lattice is not distributive.
			
	\begin{columns}
		\column{0.5\textwidth}
		\center
		\begin{tikzpicture}
			\draw[thin, ->] (-1,0) -- (1,0)node[right]{$\mathbb{C}$};
			\draw[thin, ->] (0,-1) -- (0,1)node[above]{$\mathbb{C}$};
			\draw[thick] (-1,-1) -- (1,1) node[above right]{$P$};
			\draw[thick] (-1,1) -- (1,-1) node[below right]{$P'$};
		\end{tikzpicture}
		\column{0.5\textwidth}
		\center
		\begin{tikzpicture}
			\draw[thin, ->] (-1,0) -- (1,0)node[right]{$\mathbb{C}$};
			\draw[thin, ->] (0,-1) -- (0,1)node[above]{$\mathbb{C}$};
			\draw[thick] (-1,-1) -- (1,1) node[above right]{$P$};
			\draw[thick] (-1,0.5) -- (1,-0.5) node[below right]{$Q$};
		\end{tikzpicture}
	\end{columns}

\end{frame}
	
\begin{frame}[allowframebreaks]
	
	\frametitle{References}
	
	\nocite{Reyes2013}

	\bibliography{../Mendeley/library}
	\bibliographystyle{apalike}

\end{frame}

\end{document}